Bioverse: Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2024-11-20 src/tex/ms.tex
fix references

\subsection{Fraction of inhabited planets with detectable biosignatures}
%\subsection{H1: Life only originates in hydrothermal vents}
%The hydrothermal vent scenario does not allow oceans deep enough to form an impenetrable layer of high-pressure ice on its floor.
%The resulting allowed parameter space is described by a lower limit on the bulk density. \todo[inline]{+ exclude atmospheric signature for water worlds?}
%...
%
%\subsection{H2: Life only originates in subaerial ponds with wet/dry cycles}
%We parametrize the required exposed land surface in this scenario as a lower limit in bulk density that is higher than for H1.
%Further, the tidal locking timescale of the planet may not be smaller than the age of the system.
%...
%
%\subsection{H3: Life only originates on planets with particular UV irradiance}
%\todo[inline]{\citet{Guenther2020} relate U-band energy to bolometric flux.}
%\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
%This test requires the detection of multiple biosignatures.''
%~\\
%Test for negative correlations as well?}
Here, we conduct a theoretical experiment on the UV~Threshold Hypothesis (Sect.~\ref{sec:predictions}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation at a flux exceeding a threshold $F_\mathrm{NUV, min}$.

@@

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To test the UV~Threshold Hypothesis, we require that life occurs only on planets with sufficient past UV irradiation exceeding the origins of life threshold $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
All common Origin of Life scenarios require water as a solvent;
we thus consider only rocky planets that may sustain liquid water on their surface, i.e., that occupy their host star's momentary \gls{HZ} during the above period, as well as at the epoch of observation. \todo[inline]{Does this need more detailed explanation?}
To determine \gls{HZ} occupancy, we take into account the evolution of the host star's luminosity and \gls{HZ} boundaries.

@@

\subsubsection{Existence of an atmosphere-crust interface}
By its nature, cyanosulfidic scenario relies on rock surfaces exposed to the planetary atmosphere.
Water worlds that have their entire planeary surface covered by oceans contradict this requireent and do not allow for the wet-dry cycling inherent to this origin of life scenario.
The competition of tectonic stress with gravitational crustal spreading~\citep{Melosh2011} sets the maximum possible height of mountains, which in the solar system does not exceed $\SI{\sim 20}{\kilo\meter}$.
Such mountains will be permanently underwater on water worlds.
Another impediment to wet-dry cycles may be tidal locking of the planet as it stalls stellar tide-induced water movement and diurnal irradiation variability. CITE!

>>>>

\subsection{Fraction of inhabited planets with detectable biosignatures}
%\subsection{H1: Life only originates in hydrothermal vents}
%The hydrothermal vent scenario does not allow oceans deep enough to form an impenetrable layer of high-pressure ice on its floor.
%The resulting allowed parameter space is described by a lower limit on the bulk density. \todo[inline]{+ exclude atmospheric signature for water worlds?}
%...
%
%\subsection{H2: Life only originates in subaerial ponds with wet/dry cycles}
%We parametrize the required exposed land surface in this scenario as a lower limit in bulk density that is higher than for H1.
%Further, the tidal locking timescale of the planet may not be smaller than the age of the system.
%...
%
%\subsection{H3: Life only originates on planets with particular UV irradiance}
%\todo[inline]{\citet{Guenther2020} relate U-band energy to bolometric flux.}
%\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
%This test requires the detection of multiple biosignatures.''
%~\\
%Test for negative correlations as well?}
Here, we conduct a theoretical experiment on the UV~Threshold Hypothesis by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation at a flux exceeding a threshold $F_\mathrm{NUV, min}$.

@@

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To test the UV~Threshold Hypothesis, we require that life occurs only on planets with sufficient past UV irradiation exceeding the origins of life threshold $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
All common Origin of Life scenarios require water as a solvent;
we thus consider only rocky planets that may sustain liquid water on their surface, i.e., that occupy their host star's momentary \gls{HZ} during the above period, as well as at the epoch of observation.
To determine \gls{HZ} occupancy, we take into account the evolution of the host star's luminosity and \gls{HZ} boundaries.

@@

\subsubsection{Existence of an atmosphere-crust interface}
By its nature, cyanosulfidic scenario relies on rock surfaces exposed to the planetary atmosphere.
Water worlds that have their entire planeary surface covered by oceans contradict this requireent and do not allow for the wet-dry cycling inherent to this origin of life scenario.
The competition of tectonic stress with gravitational crustal spreading~\citep{Melosh2011} sets the maximum possible height of mountains, which in the solar system does not exceed $\SI{\sim 20}{\kilo\meter}$.
Such mountains will be permanently underwater on water worlds.
Another impediment to wet-dry cycles may be tidal locking of the planet as it stalls stellar tide-induced water movement and diurnal irradiation variability~\citep[e.g.,][]{Ranjan2017b}.
